\jolideco: Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise

### 2023-01-31 src/tex/ms.tex
[showyourwork] overleaf sync

% Filler text
\usepackage{blindtext}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{showyourwork}
\usepackage{amssymb}
cd ..
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\chandra}{\textit{Chandra}~}
\newcommand{\xmm}{\textit{XMM}~}
\newcommand{\fermi}{\textit{Fermi}-LAT~}
\newcommand{\jolideco}{\textit{Jolideco}~}
\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}

@@

    \subsubsection{Image Normalisation}
    Astromomical images typically show a much higher dynamic range compared to 
    natural images. This is mostly due to the existence of point sources, which rarely occur
    in natural images, but a very common in astronomical images because of objects 
    at hig distances.
    The GMM patch prior is learned on normalized images, where the intensity values
    are constrained between 0 and 1. To evaluate For the likelihood term the image
    intensity need to be conserved.

@@

    \subsection{Deep \chandra Observation}

    \subsection{Combined \xmm and \chandra Observation}

    \subsection{\fermi Event Classes}

>>>>

% Filler text
\usepackage{blindtext}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{showyourwork}
\usepackage{amssymb}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\chandra}{\textit{Chandra}~}
\newcommand{\xmm}{\textit{XMM}~}
\newcommand{\fermi}{\textit{Fermi}-LAT~}
\newcommand{\jolideco}{\textit{Jolideco}~}
\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}

@@

    \subsubsection{Image Normalisation}
    Astronomical images typically show a much higher dynamic range compared to 
    natural images. This is mostly due to the existence of real point sources, which rarely occur
    in natural images, but a very common in astronomical images because of compact objects 
    at high distances. The high dynamic range challenges any image reconstruction
    algorithm.

    The GMM patch prior is learned on normalized images, where the intensity values
    are constrained between 0 and 1. To evaluate the GMM patch prior on the 
    model image $\mathbf{x}$ the pixel values of $\mathbf{x}$  need to be mapped 
    in the same dynamic range between 0 and 1.

    \begin{figure}[ht!]
        \script{image-norms.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/image-norms.pdf}
            \caption{
                Various image norms with different dynamic behaviour.
            }
            \label{fig:patches}
        \end{centering}
    \end{figure}

@@

    \subsection{Deep \chandra Observation}
    \begin{figure*}[ht!]
        \script{example-chandra.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/example-chandra.pdf}
            \caption{
                Chandra Example
            }
            \label{fig:example-chandra}
        \end{centering}
    \end{figure*}

    \subsection{Combined \xmm and \chandra Observation}
    \begin{figure*}[ht!]
        \script{example-xmm-chandra.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/example-xmm-chandra.pdf}
            \caption{
                Chandra Example
            }
            \label{fig:example-xmm-chandra}
        \end{centering}
    \end{figure*}

    \subsection{\fermi Event Classes}
    \begin{figure*}[ht!]
        \script{example-fermi-lat.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/example-fermi-lat.pdf}
            \caption{
                Chandra Example
            }
            \label{fig:example-fermi-lat}
        \end{centering}
    \end{figure*}
